A Standard Engineer's Shop

### 2023-11-11 Preparation/shop_tools.qmd
Reorganizing

---
title: "A Standard Engineer's Shop"
format: html
editor: visual
bibliography: references.bib
---

@@

::: {#fig-shop-layout layout-ncol=2}

![Shop Bench Tool rack](fig/PXL_20231110_190517827.jpg)

![Shop Side Tool rack](fig/PXL_20231110_190522765.jpg)

We consider only tools which might be easily used for wire cutting that are easily available.

:::

@@

![A sample of stranded wire of unknown gauge.](fig/wire_stranded.png)

@@

\begin{align}
1 \text{ comp} & P(\text{Random match}) = 0.003 \\
& P(\text{No random match}) = 0.997\\
N \text{ comp} &  P(\text{no random matches in} N \text{ comp}) = 0.997^N\\
& P(\text{at least one random match in} N \text{ comp}) = 1 - 0.997^N = `r sprintf("%.06f", 1-0.997^comparisons)`
\end{align}

In fact, if we want to control for the overall random match probability amid $N$ comparisons, we can calculate what our estimated RMP for a single comparison might be:

@@

\begin{align}
P(R_1) = r
P(\overline{R_1}) = 1-r
P(R_n) = \left[1-r\right]^n
P(\overline{R_n}) = 1 - \left[P(\overline{R_1})\right]^n = 1 - \left[1 - r\right]^n
\end{align}

Thus, if we wish to control $P(R_n)$, we can calculate out $r$ accordingly: $$r = 1 - \left[1-P(R_n)\right]^{1/n}$$

>>>>

---
title: "A Standard Engineer's Shop"
format: html
editor: visual
bibliography: ../references.bib
---

@@

::: {#fig-shop-layout layout-ncol="2"}
![Shop Bench Tool rack](../fig/PXL_20231110_190517827.jpg)

![Shop Side Tool rack](../fig/PXL_20231110_190522765.jpg)

We consider only tools which might be easily used for wire cutting that are easily available.
:::

@@

![A sample of stranded wire of unknown gauge.](../fig/wire_stranded.png)

@@

```{=tex}
\begin{align}
1 \text{ comp} & P(\text{Random match}) = 0.003 \\
& P(\text{No random match}) = 0.997\\
N \text{ comp} &  P(\text{no random matches in} N \text{ comp}) = 0.997^N\\
& P(\text{at least one random match in} N \text{ comp}) = 1 - 0.997^N = `r sprintf("%.06f", 1-0.997^comparisons)`
\end{align}
```
In fact, if we want to control for the overall random match probability amid $N$ comparisons, we can calculate what our estimated RMP for a single comparison might be:

@@

```{=tex}
\begin{align}
P(R_1) = r
P(\overline{R_1}) = 1-r
P(R_n) = \left[1-r\right]^n
P(\overline{R_n}) = 1 - \left[P(\overline{R_1})\right]^n = 1 - \left[1 - r\right]^n
\end{align}
```
Thus, if we wish to control $P(R_n)$, we can calculate out $r$ accordingly: $$r = 1 - \left[1-P(R_n)\right]^{1/n}$$
